Plotting Marker Locations in Genome

### 2025-03-26 001-map-of-samples.Rmd
First pass at cleaning up output_lists

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  # inputs:
  input_list <- list(
    oregon_rivers = "inputs/Rivers_OR/Rivers_OR.shp"
  )
  # outputs:
  output_list <- list(
    map = "results/map_of_samples/map.pdf",
    cropmap = "results/map_of_samples/map-crop.pdf",
    texmap = "tex/images/map-crop.pdf"
  )
}

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  # inputs:
  input_list <- list(
    oregon_rivers = "inputs/Rivers_OR/Rivers_OR.shp"
  )
  # outputs:
  output_list <- list(
    texmap = "tex/images/map-crop.pdf"
  )
}

# add the other entries based on the final texmap
output_list$map = "results/map_of_samples/map.pdf"
output_list$cropmap = "results/map_of_samples/map-crop.pdf"

### 2025-03-26 002-GSI_and_Fst.Rmd
First pass at cleaning up output_lists

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    map_notations = "inputs/map-notations.tsv"
  )
  # outputs:
  output_list <- list(
    assig_table = "results/GSI_and_Fst/assignment-table-full-baseline.pdf",
    fst_table = "results/GSI_and_Fst/full-baseline-but-no-lfar-Fst-table.pdf",
    assig_table_lfar_all = "results/GSI_and_Fst/assignment-table-full-baseline-plus-lfar.pdf",
    ass_table80 = "results/GSI_and_Fst/ass-table-80.pdf",
    rosa_gsi_table = "results/GSI_and_Fst/rosa-gsi-table.pdf",
    tex_table = "tex/inputs/samples-table.tex",
    gsi_fst_fig = "results/GSI_and_Fst/gsi_and_fst_fig.pdf",
    gsi_fst_fig_crop = "results/GSI_and_Fst/gsi_and_fst_fig-crop.pdf",
    gsi_fst_fig_tex = "tex/images/gsi_and_fst_fig-crop.pdf",
    ass_table80_crop = "results/GSI_and_Fst/ass-table-80-crop.pdf",
    ass_table80_tex = "tex/images/ass-table-80-crop.pdf",
    rosa_gsi_table_crop = "results/GSI_and_Fst/rosa-gsi-table-crop.pdf",
    rosa_gsi_table_tex = "tex/images/rosa-gsi-table-crop.pdf",
    pop_gen_by_loc_coll = "tex/supp_data/Supp-Data-2-pop-gen-summaries-by-locus-and-collection.csv",
    popgen_summ = "tex/inputs/popgen-summary.tex"
  )
}

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    map_notations = "inputs/map-notations.tsv"
  )
  # outputs:
  output_list <- list(
    tex_table = "tex/inputs/samples-table.tex",
    gsi_fst_fig_tex = "tex/images/gsi_and_fst_fig-crop.pdf",
    ass_table80_tex = "tex/images/ass-table-80-crop.pdf",
    rosa_gsi_table_tex = "tex/images/rosa-gsi-table-crop.pdf",
    pop_gen_by_loc_coll = "tex/supp_data/Supp-Data-2-pop-gen-summaries-by-locus-and-collection.csv",
    popgen_summ = "tex/inputs/popgen-summary.tex"
  )
}

# then add the intermediates to it:
# then add the intermediate things to it
output_list <- c(
  output_list,
  assig_table = "results/GSI_and_Fst/assignment-table-full-baseline.pdf",
  fst_table = "results/GSI_and_Fst/full-baseline-but-no-lfar-Fst-table.pdf",
  assig_table_lfar_all = "results/GSI_and_Fst/assignment-table-full-baseline-plus-lfar.pdf",
  ass_table80 = "results/GSI_and_Fst/ass-table-80.pdf",
  rosa_gsi_table = "results/GSI_and_Fst/rosa-gsi-table.pdf",
  gsi_fst_fig = "results/GSI_and_Fst/gsi_and_fst_fig.pdf",
  gsi_fst_fig_crop = "results/GSI_and_Fst/gsi_and_fst_fig-crop.pdf",
  ass_table80_crop = "results/GSI_and_Fst/ass-table-80-crop.pdf",
  rosa_gsi_table_crop = "results/GSI_and_Fst/rosa-gsi-table-crop.pdf"
)

### 2025-03-26 003-ckmr-sim-evaluation.Rmd
First pass at cleaning up output_lists

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  output_list <- list(
    ckmr_figure = "results/ckmr-sim-eval/fpr-fnr-figure.pdf",
    ckmr_figure_crop = "results/ckmr-sim-eval/fpr-fnr-figure-crop.pdf",
    ckmr_figure_tex = "tex/images/fpr-fnr-figure-crop.pdf",
    ckmr_comp = "results/ckmr-sim-eval/cmkr-comp-figure.pdf",
    ckmr_comp_crop = "results/ckmr-sim-eval/cmkr-comp-figure-crop.pdf",
    ckmr_comp_tex = "tex/images/cmkr-comp-figure-crop.pdf",
    frh_comp = "results/ckmr-sim-eval/frh-comp-figure.pdf",
    frh_comp_crop = "results/ckmr-sim-eval/frh-comp-figure-crop.pdf",
    frh_comp_tex = "tex/images/frh-comp-figure-crop.pdf"

  )
}

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  output_list <- list(
    ckmr_figure_tex = "tex/images/fpr-fnr-figure-crop.pdf",
    ckmr_comp_tex = "tex/images/cmkr-comp-figure-crop.pdf",
    frh_comp_tex = "tex/images/frh-comp-figure-crop.pdf"
  )
}

# add the intermediates that are not really outputs
output_list <- c(
  output_list,
  ckmr_figure = "results/ckmr-sim-eval/fpr-fnr-figure.pdf",
  ckmr_figure_crop = "results/ckmr-sim-eval/fpr-fnr-figure-crop.pdf",
  ckmr_comp = "results/ckmr-sim-eval/cmkr-comp-figure.pdf",
  ckmr_comp_crop = "results/ckmr-sim-eval/cmkr-comp-figure-crop.pdf",
  frh_comp = "results/ckmr-sim-eval/frh-comp-figure.pdf",
  frh_comp_crop = "results/ckmr-sim-eval/frh-comp-figure-crop.pdf"
)

### 2025-03-26 005-plotting-genome-locations-of-markers.Rmd
count up marker types in 005
First pass at cleaning up output_lists

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  # inputs:
  input_list <- list(
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv",
    chr_len = "inputs/Otsh_v2.0_chrom_lengths.tsv"
  )
  # outputs:
  output_list <- list(
    pdf = "results/genomic-locations-plot/gen-loc.pdf",
    pdfcrop = "results/genomic-locations-plot/gen-loc-crop.pdf",
    pdftex = "tex/images/genomic-locations-plot.pdf"
  )
}
# you can create the necessary output directories like this:
dump <- lapply(output_list, function(x)
  dir.create(dirname(x), recursive = TRUE, showWarnings = FALSE)
)
```

@@

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  # inputs:
  input_list <- list(
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv",
    chr_len = "inputs/Otsh_v2.0_chrom_lengths.tsv"
  )
  # outputs:
  output_list <- list(
    pdf = "results/genomic-locations-plot/gen-loc.pdf"
  )
}

# add the intermediate results/paths we need
output_list <- c(
  output_list,
  pdfcrop = "results/genomic-locations-plot/gen-loc-crop.pdf",
  pdftex = "tex/images/genomic-locations-plot.pdf"
)

# you can create the necessary output directories like this:
dump <- lapply(output_list, function(x)
  dir.create(dirname(x), recursive = TRUE, showWarnings = FALSE)
)
```

@@

Let's make a quick tally of what we have here.
```{r}
amplicons %>%
  count(LocusOrigin)
```
